Parsing Postfix log files

### 2009-02-23 doc/logparser-acronyms.tex
Annotated all URLs with last checked date.
Dealt with a couple of XXX items, and removed another couple because they're unimportant or I don't understand them any more.

\newglossaryentry{SQL}{
    type=\acronymtype,
    name={SQL},
    description={Structured Query Language},
    first={Structured Query Language (SQL)}
}
\newglossaryentry{SQL glossary}{
    name={Structured Query Language},
    description={
        The standard language used for database querying, modification, and
        maintenance.  Some information and history can be found at
        \urlLastChecked{http://en.wikipedia.org/wiki/SQL}{XXX}; a good
        introduction can be found at
        \urlLastChecked{http://philip.greenspun.com/sql/}{XXX}.
    }
}

@@

\newglossaryentry{CFL}{
    type=\acronymtype,
    name={CFL},
    description={Context Free Language},
    first={Context Free Language (CFL)}
}
\newglossaryentry{CFL glossary}{
    name={Context Free Language},
    description={
        XXX WRITE THIS DESCRIPTION
    }
}

\newglossaryentry{PDA}{
    type=\acronymtype,
    name={PDA},
    description={Push-Down Automata},
    first={Push-Down Automata (PDA)}
}
\newglossaryentry{PDA glossary}{
    name={Push-Down Automata},
    description={
        XXX WRITE THIS DESCRIPTION
    }
}

>>>>

\newglossaryentry{SQL}{
    type=\acronymtype,
    name={SQL},
    description={Structured Query Language},
    first={Structured Query Language (SQL)}
}
\newglossaryentry{SQL glossary}{
    name={Structured Query Language},
    description={
        The standard language used for database querying, modification, and
        maintenance.  Some information and history can be found at
        \urlLastChecked{http://en.wikipedia.org/wiki/SQL}{2009/02/23}; a
        good introduction can be found at
        \urlLastChecked{http://philip.greenspun.com/sql/}{2009/02/23}.
    }
}

@@

\newglossaryentry{CFG}{
    type=\acronymtype,
    name={CFG},
    description={Context Free Grammar},
    first={Context Free Grammar (CFG)}
}
\newglossaryentry{CFG glossary}{
    name={Context Free Grammar},
    description={
        See Context Free Language.
    }
}

\newglossaryentry{CFL}{
    type=\acronymtype,
    name={CFL},
    description={Context Free Language},
    first={Context Free Language (CFL)}
}
\newglossaryentry{CFL glossary}{
    name={Context Free Language},
    description={
        A Context Free Language is a language generated or parsed by a
        \acronym{CFG}.  Every transition in a CFG takes the form
        $L\rightarrow{}R$, where $L$ is a single non-terminal symbol, and
        $R$ is a (possibly empty) string of terminal and/or non-terminal
        symbols.  Every CFG can be recognised by a \acronym{PDA}.
    }
}

\newglossaryentry{PDA}{
    type=\acronymtype,
    name={PDA},
    description={Push-Down Automata},
    first={Push-Down Automata (PDA)}
}
\newglossaryentry{PDA glossary}{
    name={Push-Down Automata},
    description={
        A Push-Down Automation is a computational device similar to a
        \acronym{FA}, but it can additionally use a stack to store data.
        A PDA can manipulate the stack during state transitions (adding or
        removing a single piece of data), and can use 
        the piece of data on the top of the stack in addition to the input
        when determining which state transition to take.  PDA can recognise
        languages of the form $a^{n}b^{n}$, i.e.\ any number of one symbol
        followed by the same number of another symbol.
    }
}
